Transition path sampling based calculations of free energies for enzymatic reactions: the case of human methionine adenosyl transferase and plasmodium vivax adenosine deaminase

### 2022-06-05 tex/manuscript.tex
changes made to the manuscript

$pv$ADA catalyzes the reaction between adenosine and OH$^{-}$ ion 
resulting in the formation of inosine and ammonia as shown in
Fig. \ref{fig:ada-reaction}.
The nucleophilic O atom of the OH$^{-}$ anion
attacks the electrophilic C6 atom of the adenosyl ring leading to the 
formation of a Meisenheimer complex like structure while the N1 atom 
on the adenosyl moiety gets protonated by the Glu229 residue of $pv$ADA. 
The key bond parameters are the distance between the approaching hydroxyl 
oxygen and the C6 atom (denoted as d$_{\text{OC}}$) and the 
dissociating C6$-$N6 (d$_{\text{NC}}$) bond distance. For the TPS simulations 
we define the reactant state to have d$_{\text{NC}}$ being less than $1.8$ {\AA} 
and the product state to have the d$_{\text{OC}}$ less than $1.8$ {\AA}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ada-new-reaction.png}
\caption{The reaction catalyzed by the $pv$ADA enzyme between adenosine and hydroxide ion
resulting in the formation of inosine and ammonia.}
\label{fig:ada-reaction}
\end{figure}

@@

\includegraphics[scale=0.12]{blender-images/ada/mat2a-trans-labelled.png}

@@

\includegraphics[scale=0.12]{blender-images/ada/new-ada-trans.png}

@@

\includegraphics[scale=1.0]{./figures/ada-fenergy.pdf}

>>>>

$pv$ADA catalyzes the reaction between adenosine and OH$^{-}$ anion
resulting in the formation of inosine and ammonia as shown in
Fig. \ref{fig:ada-reaction}.
The nucleophilic O atom of the OH$^{-}$ anion
attacks the electrophilic C6 atom of the adenosyl ring leading to the 
formation of a Meisenheimer complex like structure while the N1 atom 
on the adenosyl moiety gets protonated by the Glu229 residue of $pv$ADA. 
The key bond parameters are the distance between the approaching hydroxyl 
oxygen and the C6 atom (denoted as d$_{\text{OC}}$) and the 
dissociating C6$-$N6 (d$_{\text{NC}}$) bond distance. For the TPS simulations 
we define the reactant state to have d$_{\text{NC}}$ being less than $1.8$ {\AA} 
and the product state to have the d$_{\text{OC}}$ less than $1.8$ {\AA}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ada-reaction.png}
\caption{The reaction catalyzed by the $pv$ADA enzyme between adenosine and hydroxide ion
resulting in the formation of inosine and ammonia.}
\label{fig:ada-reaction}
\end{figure}

@@

\includegraphics[scale=0.12]{figures/mat2a-trans-labelled.png}

@@

\includegraphics[scale=0.12]{figures/new-ada-trans.png}

@@

\includegraphics[scale=1.0]{figures/ada-fenergy.pdf}
